Anxiety: a decision-theoretic perspective

### 2019-01-03 manuscript/manuscript.tex
progress on open field demonstration/text

\title{something something about anxiety}

@@

>>>>

\title{Anxiety: a decision-theoretic perspective}

@@

First and foremost, pathological anxiety is associated with pessimistic expectations
about the probability and cost of future negative events (Grupe \& Nitschke, 2013;
Bishop \& Gagne, 2018). In fear conditioning, individuals with anxiety are more
likely to exhibit increased threat appraisal for safety signals (CS-) and the
extinguished fear cue (CS+) (Lissek et al. 2005; Duits et al., 2015). In considering
hypothetical future negative outcomes, individuals with anxiety are more likely
to evaluate negative outcomes as more likely and their consequences more severe
(pick a few references).

Importantly, in the clinical literature, pathological anxiety is also associated
with a lack of perceived control (Gallagher et al., 2014). Studies suggest that
this belief mediates anxiety (ref?). This can come in whatever form.

In the first series of simulations, we show directly how lack of perceived control
can directly account for pessimistic inference. In the open field environment
(Figure 1a), an agent navigates a simple grid-world. The world consists of almost
entirely of empty tiles, except for two which yield a reward and punishment,
respectively.

Under complete control (objective or perceived), an agent in this environment is
under no threat despite the presence of an aversive state. This is simply because,
in a full controllable world, a (non-masochistic) agent is never forced to interact
with the aversive state. When this control breaks down -- through a stochastic
world or a distrust of future competency -- an agent can no longer guarantee it
will never encounter the aversive state. In such a scenario, the negative value
back-propagates to its predecessor states through the recursive formulas defined
above. The result is an environment that appears worse (i.e. less positive) than
it otherwise would.

We shoe this above. Using value iteration. Show it for best-case scenario. Show
it for expected random. Show it for worst-case scenario.

\begin{figure}
  \centerline{%
    \resizebox{1.0\textwidth}{!}{\includegraphics[trim={0 0 0 0},clip]{../figures/01_field.png}}%
  }
  \caption{\textbf{Open Field Environment}}
  \par Oooh so pretty.
\end{figure}
